R Notebook

### 2020-11-24 FEM_R/model_analysis.Rmd
Implemented the reactable tables for T-tests and happy with the output

```{r setup, include=FALSE}
# Need to set up the environment
workingDir <- "/home/luke/Documents/E_FEM_clean/E_FEM/output/"
knitr::opts_knit$set(root.dir = workingDir)

@@

First, we will collect and present all the T-tests together. We will add the prefix 'min_' or 'cv_' onto the variable names so we don't get mixed up.

```{r}
# names for T-tests directory and filename stem
min <- "ELSA_minimal/T-tests/"
stem <- "minimal_all_waves_"

@@

# Collect in a list to do some formatting
min_list <- list(min_uw, min_demog, min_binhlth, min_binecon, min_risk)
# Add prefix 'min_' onto every variable name for clarity
min_list <- lapply(min_list, rename_first_var, prefix='min')
# Rename columns to be more succinct
min_list <- lapply(min_list, shorten_columns)

@@

```{r}
# names for T-tests directory and filename stem
CV1 <- "ELSA_CrossValidation1/T-tests/"
stem <- "CV1_all_waves_"
# Read in files
cv_uw <- read.csv(paste0(CV1, stem, "unweighted.csv"))
cv_demog <- read.csv(paste0(CV1, stem, "demog.csv"))
cv_binhlth <- read.csv(paste0(CV1, stem, "binhlth.csv"))
cv_binecon <- read.csv(paste0(CV1, stem, "binecon.csv"))
cv_risk <- read.csv(paste0(CV1, stem, "risk.csv"))
# Now collect into list and rename vars and cols for clarity
cv_list <- list(cv_uw, cv_demog, cv_binhlth, cv_binecon, cv_risk)
cv_list <- lapply(cv_list, rename_first_var, prefix='CV')
cv_list <- lapply(cv_list, shorten_columns)
```

Both Minimal and Cross-validation T-tests are now renamed and collected into a separate list object each. We will now combine like tests together (i.e. demog with demog, binhlth with binhlth).

@@

### Unweighted (died)
```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
uw <- rbind(min_list[[1]], cv_list[[1]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
uw <- arrange(uw, Variable)
#uw
formattable(uw, 
            align = c('l', rep('r', ncol(uw) - 1)),
            list(area(col=pValNames) 
                  ~ proportion_bar(color='green', 0.01)))
```
### Demographics
```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
demog <- rbind(min_list[[2]], cv_list[[2]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
demog <- arrange(demog, Variable)
formattable(demog, 
            align = c('l', rep('r', ncol(demog) - 1)),
            list(area(col=pValNames) 
                  ~ proportion_bar(color='green', 0.01)))
```
### Binary Health
```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
binhlth <- rbind(min_list[[3]], cv_list[[3]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
binhlth <- arrange(binhlth, Variable)
formattable(binhlth, 
            align = c('l', rep('r', ncol(binhlth) - 1)),
            list(area(col=pValNames) 
                  ~ proportion_bar(color='green', 0.01)))
```
### Binary Economic
```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
binecon <- rbind(min_list[[4]], cv_list[[4]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
binecon <- arrange(binecon, Variable)
formattable(binecon, 
            align = c('l', rep('r', ncol(binecon) - 1)),
            list(area(col=pValNames) 
                  ~ proportion_bar(color='green', 0.01)))
```
### Risk Behaviours
```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
risk <- rbind(min_list[[5]], cv_list[[5]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
risk <- arrange(risk, Variable)
formattable(risk, 
            align = c('l', rep('r', ncol(risk) - 1)),
            list(area(col=pValNames) 
                  ~ proportion_bar(color='green', 0.01)))
```

@@

# Reactable Package

```{r}

stickyStyle <- list(position = "sticky", left = 0, background = "#fff", zIndex = 1,
                    borderRight = "1px solid #eee")

reactable(risk,
          defaultColDef = colDef(
            header = function(value) gsub('_', ' ', value, fixed=TRUE),
            cell = function(value) format(value, nsmall = 2),
            align='center',
            headerStyle = list(background = "#f7f7f8")
          ),
          columns = list(
            Variable = colDef(minWidth = 160,
                              style = stickyStyle,
                              headerStyle = stickyStyle)
          ),
          bordered = TRUE,
          highlight = TRUE,
          striped = TRUE)

>>>>

```{r setup, include=FALSE}
# Need to set up the working directory
workingDir <- "/home/luke/Documents/E_FEM_clean/E_FEM/output/"
knitr::opts_knit$set(root.dir = workingDir)

@@

<!-- First, we will collect and present all the T-tests together. We will add the prefix 'min_' or 'cv_' onto the variable names so we don't get mixed up. -->

```{r include=FALSE}
# names for T-tests directory and filename stem
min <- "ELSA_minimal/T-tests/"
stem <- "minimal_all_waves_"

@@

# Collect in a list to do some formatting
min_list <- list(min_uw, min_demog, min_binhlth, min_binecon, min_risk)
# Add prefix 'min_' onto every variable name for clarity
min_list <- lapply(min_list, rename_first_var, prefix='min')
# Rename columns to be more succinct
min_list <- lapply(min_list, shorten_columns)
# Replace na with 0
min_list <- lapply(min_list, function(x) { x[is.na(x)] <- 0; x} )

@@

```{r include=FALSE}
# names for T-tests directory and filename stem
CV1 <- "ELSA_CrossValidation1/T-tests/"
stem <- "CV1_all_waves_"
# Read in files
cv_uw <- read.csv(paste0(CV1, stem, "unweighted.csv"))
cv_demog <- read.csv(paste0(CV1, stem, "demog.csv"))
cv_binhlth <- read.csv(paste0(CV1, stem, "binhlth.csv"))
cv_binecon <- read.csv(paste0(CV1, stem, "binecon.csv"))
cv_risk <- read.csv(paste0(CV1, stem, "risk.csv"))
# Now collect into list and rename vars and cols for clarity
cv_list <- list(cv_uw, cv_demog, cv_binhlth, cv_binecon, cv_risk)
cv_list <- lapply(cv_list, rename_first_var, prefix='CV')
cv_list <- lapply(cv_list, shorten_columns)
cv_list <- lapply(cv_list, function(x) { x[is.na(x)] <- 0; x} )
```

<!-- Both Minimal and Cross-validation T-tests are now renamed and collected into a separate list object each. We will now combine like tests together (i.e. demog with demog, binhlth with binhlth). -->

@@

<!-- Lets build the combined tables now. -->

```{r include=FALSE}
# Row bind to collect both dfs together
uw <- rbind(min_list[[1]], cv_list[[1]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
uw <- arrange(uw, Variable)

# demog
demog <- rbind(min_list[[2]], cv_list[[2]])
demog <- arrange(demog, Variable)

# binhlth
binhlth <- rbind(min_list[[3]], cv_list[[3]])
binhlth <- arrange(binhlth, Variable)

# binecon
binecon <- rbind(min_list[[4]], cv_list[[4]])
binecon <- arrange(binecon, Variable)

# risk
risk <- rbind(min_list[[5]], cv_list[[5]])
risk <- arrange(risk, Variable)
```

# Reactable Tables

The [reactable](https://glin.github.io/reactable/index.html) package has the ability to include lots of complex styling, such as additional colour, formatting and even inline graphs built dynamically from the input data.

For the purpose of this document, we are going to include a sticky first column (so we can always see the variable names whilst scrolling), a colour gradient from white to green based on the P Value (low = white, high = green), and a red cell background for any P values of 0.

```{r echo = FALSE}
## This block will define the logic for creating the tables with Reactable
# The tables are formatted exaclty the same for each group of vars so makes sense to define this only once

# createTTT - create T-Test Table
# Have a default column definition, to handle the basic formatting, then specific formatting for the first column (Variable) and P Val cols
createTTT <- function(t) {
  # To enable a 'sticky' first column, that always shows as you scroll across the table
  stickyStyle <- list(position = "sticky", left = 0, background = "#fff", zIndex = 1,
                      borderRight = "1px solid #eee")

  # Define a colour ramp to use for P Value cell gradients
  greenPal <- function(x) rgb(colorRamp(c("#ffffff", "#008000"))(x), maxColorValue = 255)

  # Add in the green colour gradient for P Value cells. Also add a red block for value of 0
  pValColDef <- colDef(
    style = function(value) {
      color <- greenPal(value)
      if (value == 0) {
        color <- "#ff4c4c"
      }
      list(background = color)
    },
    minWidth = 110
  )

  res <- reactable(t,
            defaultColDef = colDef(
              header = function(value) gsub('_', ' ', value, fixed=TRUE),
              cell = function(value) format(value, nsmall = 2),
              align='center',
              style = function(value) {

              }
              #headerStyle = list(background = "#f7f7f8")
            ),
            columns = list(
              Variable = colDef(
                  minWidth = 160,
                  style = stickyStyle,
                  headerStyle = stickyStyle),
              P_Value_3 = pValColDef,
              P_Value_4 = pValColDef,
              P_Value_5 = pValColDef,
              P_Value_6 = pValColDef,
              P_Value_7 = pValColDef,
              P_Value_8 = pValColDef
            ),
            bordered = TRUE,
            highlight = TRUE,
            striped = TRUE)

  return(res)
}

### Unweighted (Died)

```{r echo = FALSE}
# Create the actual table!
uwTab <- createTTT(uw)
uwTab
```

### Demographics

```{r echo = FALSE}
# Create the actual table!
demogTab <- createTTT(demog)
demogTab
```

### Binary Health
```{r echo = FALSE}
# Create the actual table!
binhlthTab <- createTTT(binhlth)
binhlthTab
```
### Binary Economic
```{r echo = FALSE}
# Create the actual table!
bineconTab <- createTTT(binecon)
bineconTab
```
### Risk Behaviours
```{r echo = FALSE}
# Create the actual table!
riskTab <- createTTT(risk)
riskTab
```

# DEFUNKT
### Unweighted (died)
```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
uw <- rbind(min_list[[1]], cv_list[[1]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
uw <- arrange(uw, Variable)
#uw
formattable(uw, 
            align = c('l', rep('r', ncol(uw) - 1)),
            list(area(col=pValNames) 
                  ~ proportion_bar(color='green', 0.01)))
```
### Demographics
```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
demog <- rbind(min_list[[2]], cv_list[[2]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
demog <- arrange(demog, Variable)
formattable(demog, 
            align = c('l', rep('r', ncol(demog) - 1)),
            list(area(col=pValNames) 
                  ~ proportion_bar(color='green', 0.01)))
```
### Binary Health
```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
binhlth <- rbind(min_list[[3]], cv_list[[3]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
binhlth <- arrange(binhlth, Variable)
formattable(binhlth, 
            align = c('l', rep('r', ncol(binhlth) - 1)),
            list(area(col=pValNames) 
                  ~ proportion_bar(color='green', 0.01)))
```
### Binary Economic
```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
binecon <- rbind(min_list[[4]], cv_list[[4]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
binecon <- arrange(binecon, Variable)
formattable(binecon, 
            align = c('l', rep('r', ncol(binecon) - 1)),
            list(area(col=pValNames) 
                  ~ proportion_bar(color='green', 0.01)))
```
### Risk Behaviours
```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
risk <- rbind(min_list[[5]], cv_list[[5]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
risk <- arrange(risk, Variable)
formattable(risk, 
            align = c('l', rep('r', ncol(risk) - 1)),
            list(area(col=pValNames) 
                  ~ proportion_bar(color='green', 0.01)))
```

@@
